---
title: EDGI Exercise Descriptive Paper Results
author: Katherine Schaumberg
output:
  bookdown::html_document2: default
---

```{r, setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, results = 'hide')
library(expss)
library(bookdown)
library(dplyr)
library(haven)
library(sjmisc)
library(rmarkdown)
library(knitr)
library(psych)
library(ggplot2)
load('data/EDGI_exercise_cleaned.RData') 

exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_exercise_icb >0)
compulsive_exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_ex_compulsive >0)
```

# Descriptives

## Sociodemographics

Sociodemographic variables reported in the current project include age, gender, and race/ethnicity. Below are descriptions of the US sample (Total N = 7259). The majority of the US sample (84.17%) are Non-Hispanic White with minority groups represented at lower rates (Race: 2.44% Black; 2.56% Asian/Pacific Islander; 5.10% Other/Mixed Race; Ethnicity: 8.14% Hispanic/Latino).

```{r, echo=FALSE,message=FALSE, results='hide'}
#`ED100k_ethnicity_dummy_1` (Race dummy coded Non-Hispanic White vs All other) : of participants reporting race

frq(EDGI_exercise_cleaned$ED100k_ethnicity_dummy_1)

#`ED100k_ethnicity_dummy_2` (Race dummy coded White [1], Black [2], Asian/PI [3], Hispanic (non-black) [4], Other) 
frq(EDGI_exercise_cleaned$ED100k_race_dummy_2)
```
At the time of assessment, the average age of participants was
`r round(mean(EDGI_exercise_cleaned$age),2)` (SD =
`r round(sd(EDGI_exercise_cleaned$age),2)`). All participants (n = `r sum(!is.na(EDGI_exercise_cleaned$age))`)
reported their age

With regards to sex and gender, the majority of the sample (88.61%) identified as women, with 6.46% identifying as nonbinary and 4.50% identifying as men. 96.25% of the sample were assigned female at birth.

```{r}
#`gender`; 1 = Man, 2 = Woman, 3 = Nonbinary = 4 = two Spirit; 99 = Other
frq(EDGI_exercise_cleaned$gender)
frq(EDGI_exercise_cleaned$sex)
```

## Eating Disorder Diagnosis Groups

The  ED100K-v3 (Thornton et al., 2018a): self-report diagnostic questionnaire for eating disorders that is based on the Structured Clinical Interview for DSM-5 (SCID). The ED100K-v2 yields DSM-5 lifetime diagnoses of AN, BN, and BED. The ED100K has previously been validated against the SCID (Thornton et al., 2018b).

In terms of eating disorder diagnostic groupings, `r frq(EDGI_exercise_cleaned$an_case)[[1]]$valid.prc[[2]]`% of participants reported a history of symptoms consistent with a diagnosis of AN, `r frq(EDGI_exercise_cleaned$bn_case)[[1]]$valid.prc[[2]]`% of participants reported a history of symptoms consistent with a diagnosis of BN, and `r frq(EDGI_exercise_cleaned$bed_case)[[1]]$valid.prc[[2]]`% of participants reported a history of symptoms consistent with a diagnosis of BED. When taken together, 41.64% of the sample reported a history of AN only, 12.37% reported BN only, 9.1% reported BED only, 14.12% reported AN and BN, 14.44% reported BN and BED, 2.20% reported AN and BED, and 6.12% reported all three disorders. For analyses, individuals with single diagnoses are considered as independent groups. Groups with mixed diagnoses were categorized as a 'mixed, restrictive spectrum' (AN + BN, AN + BED, AN + BN + BED; 22.44%) or 'mixed, binge spectrum' (BN + BED; 14.44%)

```{r}
as.data.frame(table(EDGI_exercise_cleaned[c('an_case', 'bn_case', 'bed_case')])) |>
  mutate (prop = round(Freq/sum(Freq)*100, 2)) |> 
  filter (Freq != 0) 
#Make case heirarcy and recode restrictive and binge spectrum mixed cases
EDGI_exercise_cleaned <- EDGI_exercise_cleaned |> 
  mutate (case_status = case_when(an_case == 1 & bn_case == 0 & bed_case == 0 ~ 'AN',
                                   an_case == 0 & bn_case == 1 & bed_case == 0 ~ 'BN',
                                   an_case == 0 & bn_case == 0 & bed_case == 1 ~ 'BED', 
                                   an_case == 1 & (bn_case == 1 | bed_case == 1) ~ 'AN Mixed',
                                   an_case == 0 & bn_case ==1 & bed_case ==1 ~ 'BN-BED Mixed' )) |> 
  mutate (case_heirarchy = case_when (an_case == 1 ~ 'AN', 
                                      bn_case == 1 ~ 'BN', 
                                      bed_case == 1 ~ 'BED'))
frq(EDGI_exercise_cleaned$case_status)
```

## Weight History
```{r}

WtHx<- EDGI_exercise_cleaned|> 
  select(record_id, height, wt_cur_lb, wt_lo_lb, wt_hi_lb, currentbmi, highestbmi, lowestbmi, ED100k_wt_suppress_high_current, ED100k_wt_suppress_curr_low) 

#Save data file -- 'weight history outliers' 
WtHx_outliers <- WtHx |> 
  filter(currentbmi > 70 | currentbmi < 10 | ED100k_wt_suppress_curr_low > 250 | ED100k_wt_suppress_high_current > 250 | ED100k_wt_suppress_high_current < 0 | ED100k_wt_suppress_curr_low < 0) 
write.csv(WtHx_outliers, file = 'data/EDGI_WtHx_outliers.csv')

```

There were 25 individuals who reported a current BMI > 70 or < 10 and 77 individuals who reported weight suppression values that were high (> 250 lb difference between highest weight and current weight or current weight and lowest weight, or negative weight suppression values -- i.e. a current weight that is higher than one's highest ever weight, or a lowest weight that is higher than one's current weight) 


BMIs of > 70 and < 10 were removed for data integrity. Weight history is presented in table \@ref(tab:wthx). **Note - there are some out of range values for weight suppression we have to decide what we want to do with these**

```{r wthx, results='asis', warning=FALSE}

WtHx <- WtHx |> select(-c(record_id))
  
Wthx <- describe(WtHx) |> 
  mutate(across(where(is.numeric), round, digits = 2))  
rownames(Wthx) <- c('Height', 'Current Weight', 'Lowest Weight', 'Highest Weight', 'Current BMI', 'Highest BMI', 'Lowest Adult BMI', 'Current Weight Suppression', 'Current vs.Lowest Weight')

knitr::kable(Wthx, caption = 'Weight History')
```


## Eating Disorder Variables

Eating disorder variables was assessed by three varying assessments - the ED100k; EDEQ, and CET.

### ED100k

For current paper -- we use an item from the ED100k that captures historical exercise for weight and shape control. This question asked if exercise was ever used as a behavior to intentionally control weight or shape,  with options of Never (n = 945; 13.02%), A few times, but never became a habit (n = 1710; 23.56%), and More often (n = 4604; 63.42%). 
```{r}
frq(EDGI_exercise_cleaned$ED100k_exercise_icb)
```
### EDEQ

The Eating Disorder Examination-Questionnaire (EDE-Q v 6.0) (Fairburn,
2008; Fairburn & Beglin, 1994) is a valid, reliable self-report questionnaire of cognitive and behavioral symptoms of eating disorders over the prior four weeks. The questionnaire has four subscales (Restraint, Eating Concern, Shape Concern, Weight Concern), a Global scale, and items that measure fasting (item 2), objective binge eating (item 15), self-induced vomiting (item 16), laxative use (item 17), and driven exercise (item 18), "Over the past 28 days, how many times have
you exercised in a driven or compulsive way as a means of controlling your weight, shape, or amount of fat, or to burn off calories)". `r sum(!is.na(EDGI_exercise_cleaned$edeq_global))` individuals completed at least 75% of EDEQ global items. Descriptive information for EDEQ subscales is presented in table \@ref(tab:edeq)

```{r edeq, results='asis'}
EDEQ_scales_1<- EDGI_exercise_cleaned|> 
  select(edeq_restraint, edeq_wc, edeq_ec, edeq_sc, edeq_global) 
EDEQ_scales <- describe(EDEQ_scales_1) |> 
  select(!c(vars, mad)) |> 
    mutate(across(where(is.numeric), round, digits = 2))

rownames(EDEQ_scales) <- c('Restraint', 'Weight Concern', 'Eating Concern', 'Shape Concern', 'Global')

knitr::kable(EDEQ_scales, caption = 'EDEQ Subscales')
```

With regards to eating disorder behaviors at present, individuals reported a range of ongoing ED behviors (see table \@ref(tab:edbehav)). **Note -- need to decide what to do with out of range values ** While about half (46.92%) of individuals reported any driven exercise in the past four weeks, a smaller number (13.38%) reported driven exercise more than 20 times in the past 28 days.

```{r edbehav, results='asis'}
EDEQ_behaviors_raw <- EDGI_exercise_cleaned|> 
  select(edeq_laxative_freq_28, edeq_vomit_freq_28, edeq_ex_driven_freq_28, edeq_binge_days_28, edeq_fast_freq_28_ordinal) 
EDEQ_behaviors <- describe(EDEQ_behaviors_raw) |> 
  select(!c(vars, mad)) |> 
    mutate(across(where(is.numeric), round, digits = 2))

rownames(EDEQ_behaviors) <- c('Laxative Use', 'Vomitting', 'Driven Exercise', 'Binge Eating (days)', 'Fasting (Oridnal 0-6)')
knitr::kable(EDEQ_behaviors, caption = 'EDEQ Behaviors')
```

```{r}
EDGI_exercise_cleaned <- EDGI_exercise_cleaned |> 
  mutate(edeq_ex_excessive = case_when(edeq_ex_driven_freq_28 >=20 ~ 1, 
                                    edeq_ex_driven_freq_28 < 20 ~ 0) )
frq(EDGI_exercise_cleaned$edeq_ex_excessive)
```

### CET

The Compulsive Exercise Test (CET) (Taranis et al., 2011): In response to the limitations of previous measures of compulsive exercise, Taranis et al. (2011) developed the CET. The CET is designed to facilitate tests of an empirically supported cognitive behavioral model of compulsive exercise within the context of eating disorders. The CET represented a shift in the focus of measures of compulsive exercise, as it was designed to capture the features of compulsive exercise most relevant for understanding eating disorders, rather than earlier simplistic measures which focused on quantity of exercise and did not capture psychological dependence. The CET is based on four key factors proposed to characterise compulsive exercise based on Meyer, Taranis, Goodwin, and Haycraft (2011) cognitive-behavioural model: eating psychopathology, obsessive compulsiveness, affect regulation, and perfectionism. In this model, compulsive exercise differs from healthy exercise in that compulsively exercising individuals present with weight and shape concerns, persistently continue exercising with the aim to avoid guilt or negative affect, and have very rigid, ritualistic and inflexible attitudes towards their exercising behaviour (Meyer et al., 2011). The time frame measured is current and the CET has a total score and five subscales. There is also a clinical cutoff defined for the scale, which can be used to define CE presence vs. absence. 

Only a subset (n = `r sum(!is.na(EDGI_exercise_cleaned$cet_total_complete))`) of participants
completed the CET

Subscale and total score information for the CET is presented in Table \@ref(tab:cet). Of those completing the CET, about a third (34.38%), met clinical cutoff for *current* compulsive exercise.

```{r cet, results='asis'}
CET_scales_1<- EDGI_exercise_cleaned|> 
  select(cet_avoid, cet_wtcontrol, cet_rigid, cet_mood, cet_enjoy, cet_total_complete) 
CET_scales <- describe(CET_scales_1) |> 
  select(!c(vars, mad)) |> 
      mutate(across(where(is.numeric), round, digits = 2))

rownames(CET_scales) <- c('Avoidance and Rule-Driven Behavior', 'Weight Control', 'Rigidity', 'Mood Improvement', 'Lack of Enjoyment', 'Total')

knitr::kable(CET_scales, caption = 'CET Subscales')
```
```{r, echo=FALSE, message=FALSE}
frq(EDGI_exercise_cleaned$cet_clinical)
```
# Maladaptive Exercise across Diagnosis, Age, Gender, and Weight History

Considering across diagnosis, the following describes rates of (1) maladaptive exercise history; (2) rates of CET clinical cutoff being met, and (3) current CET symptom scores

## Diagnosis Groups

```{r}
ct <- table(EDGI_exercise_cleaned$case_status, EDGI_exercise_cleaned$ED100k_exercise_icb_factor)

dx_row_percents <- prop.table (ct, 1)

dx_row_percents <- as.data.frame(dx_row_percents) |> 
 rename(`Diagnosis Group` = Var1) |> 
 rename(`History of Driven Exercise` =Var2) 

ggplot(dx_row_percents, aes( x = `History of Driven Exercise`, y = Freq*100, fill = `Diagnosis Group` )) + 
  geom_col()+
  facet_wrap (~ `Diagnosis Group`) +
  labs(title = 'Percentages by Diagnosis Group and History of Driven Exercise', x = 'History of Driven Exercise', y = 'Percentage (within Diagnosis Group)') + 
  scale_x_discrete(labels = c('Never', 'A few', 'More Often')) +
    theme(legend.position = 'none') 

```

### CET Clinical Cutoff

```{r}
cet_clinical <- table(EDGI_exercise_cleaned$case_status, EDGI_exercise_cleaned$cet_clinical)

dx_row_percents_cet <- prop.table (cet_clinical, 1)

dx_row_percents_cet <- as.data.frame(dx_row_percents_cet) |> 
 rename(`Diagnosis Group` = Var1) |> 
 rename(`CET Clinical Cutoff Met` =Var2) |> 
 filter(`CET Clinical Cutoff Met` == 1)

ggplot(dx_row_percents_cet, aes( x = `Diagnosis Group`, y = Freq*100, fill = `Diagnosis Group` )) + 
  geom_col()+
  labs(title = 'Percentage of Current CET Cutoff Met by Diagnosis Group', x = 'History of Driven Exercise', y = 'Percentage (within Diagnosis Group)') + 
theme(legend.position = 'none') 


```
```{r}
median_cet <- EDGI_exercise_cleaned |> 
  group_by (case_status) |> 
  summarize (median_cet = median (cet_total_weighted_sum, na.rm = TRUE))

cet_plot <- ggplot(EDGI_exercise_cleaned, aes(x = case_status, y = cet_total_weighted_sum, color = case_status)) +
  geom_jitter(size = 0.3) +
  geom_boxplot(alpha = 0.5, color= 'black') +
  labs(title = 'Current CET score based on Diagnosis History', x = 'Diagnosis Group', y = 'CET score') + 
  theme(legend.position = 'none') +
  geom_text(data = median_cet, aes(x = case_status, y = median_cet + 1, label = round(median_cet, 1)), size = 3, color = 'black', fontface ='bold')


cet_plot
```


## Age
```{r}

median_age <- EDGI_exercise_cleaned |> 
  group_by (ED100k_exercise_icb_factor, case_status) |> 
  summarize (median_age = median (age, na.rm = TRUE))

age_plot <- ggplot(EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = age, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color= 'black') +
  facet_wrap(~case_status) +
  labs(title = 'Age based on Diagnosis History and History or of DEx', x = 'History of Driven Exercise', y = 'Age') + 
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) + 
  theme(legend.position = 'none') + 
  geom_text(data = median_age, aes(x = ED100k_exercise_icb_factor, y = median_age + 2, label = median_age), size = 3, color = 'black', fontface ='bold')

age_plot
```
```{r}
ggplot(data = EDGI_exercise_cleaned, aes(x= age, y = cet_total_weighted_sum))+  
  geom_point() + 
  geom_smooth(method = 'lm', color = 'red')
```


## Gender
```{r}
exh_gender <- table(EDGI_exercise_cleaned$ED100k_gender_dummy, EDGI_exercise_cleaned$ED100k_exercise_icb_factor)

gender_row_percents <- prop.table (exh_gender, 1)

gender_row_percents <- as.data.frame(gender_row_percents) |> 
 rename(`Gender` = Var1) |> 
 rename(`History of Driven Exercise` =Var2) 

names(gender_row_percents$Gender) <- c('Male', 'Female', 'Nonbinary')

ggplot(gender_row_percents, aes( x = `History of Driven Exercise`, y = Freq*100, fill = Gender )) + 
  geom_col()+
  facet_wrap (~ Gender) +
  labs(title = 'History of Driven Exercise across Gender', x = 'History of Driven Exercise', y = 'Percentage (within Gender)') + 
  scale_x_discrete(labels = c('Never', 'A few', 'More Often'))  +
  theme(legend.position = 'none') 


```

## Weight History 

```{r}
EDGI_exercise_cleaned <- EDGI_exercise_cleaned |> 
  mutate (currentbmi = if_else(currentbmi > 70 | currentbmi < 10, NaN, currentbmi)) |> 
  mutate (lowestbmi = if_else(lowestbmi > 70 | lowestbmi < 10, NaN, lowestbmi)) |> 
  mutate (highetbmi = if_else(highestbmi > 70 | highestbmi < 10, NaN, highestbmi)) |> 
  mutate (ED100k_wt_suppress_high_low = if_else(ED100k_wt_suppress_high_low > 250 | ED100k_wt_suppress_high_low < 0, NaN, ED100k_wt_suppress_high_low)) |> 
  mutate (ED100k_wt_suppress_curr_low = if_else(ED100k_wt_suppress_curr_low > 250 | ED100k_wt_suppress_curr_low < 0, NaN, ED100k_wt_suppress_curr_low)) |> 
  mutate (ED100k_wt_suppress_high_current= if_else(ED100k_wt_suppress_high_current > 250 | ED100k_wt_suppress_high_current < 0, NaN, ED100k_wt_suppress_high_current)) 


medians <- EDGI_exercise_cleaned |> 
  group_by (ED100k_exercise_icb_factor, case_status) |> 
  summarize (median_ws_curr_low = median (ED100k_wt_suppress_curr_low, na.rm = TRUE),
             median_current_bmi= median (currentbmi, na.rm = TRUE),
             median_highest_bmi = median(highestbmi, na.rm = TRUE),
             median_lowestbmi = median (lowestbmi, na.rm = TRUE),
             median_ws_high_low = median (ED100k_wt_suppress_high_low, na.rm = TRUE), 
             median_ws_high_current = median (ED100k_wt_suppress_high_current, na.rm = TRUE),
             median_ws_curr_low = median (ED100k_wt_suppress_curr_low, na.rm = TRUE), 
)


currbmi_plot <- ggplot(EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = currentbmi, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color= 'black') +
  facet_wrap(~case_status) +
  labs(title = 'Current BMI based on Diagnosis History and History or of DEx', x = 'History of Driven Exercise', y = 'Current BMI') + 
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) + 
  theme(legend.position = 'none') + 
  geom_text(data = medians, aes(x = ED100k_exercise_icb_factor, y = median_current_bmi + 2, label = round(median_current_bmi, 1)), size = 3, color = 'black', fontface ='bold') 

currbmi_plot

```



```{r}
lowestbmi_plot <- ggplot(EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = lowestbmi, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color= 'black') +
  facet_wrap(~case_status) +
  labs(title = 'Lowest BMI based on Diagnosis History and History or of DEx', x = 'History of Driven Exercise', y = 'Lowest BMI') + 
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) + 
  theme(legend.position = 'none') + 
  geom_text(data = medians, aes(x = ED100k_exercise_icb_factor, y = median_lowestbmi + 2, label = round(median_lowestbmi, 1)), size = 3, color = 'black', fontface ='bold') +
  scale_y_continuous(limits = c(10, 40))
  

lowestbmi_plot
```

```{r}
highestbmi_plot <- ggplot(EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = highestbmi, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color= 'black') +
  facet_wrap(~case_status) +
  labs(title = 'Highest BMI based on Diagnosis History and History or of DEx', x = 'History of Driven Exercise', y = 'Highest BMI') + 
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) + 
  theme(legend.position = 'none') + 
  geom_text(data = medians, aes(x = ED100k_exercise_icb_factor, y = median_highest_bmi + 2, label = round(median_highest_bmi, 1)), size = 3, color = 'black', fontface ='bold') +
  scale_y_continuous(limits = c(10, 70))
  

highestbmi_plot
```


```{r}
ws_plot <- ggplot (EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = ED100k_wt_suppress_high_current, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color =  'black', aes(middle = median(ED100k_wt_suppress_high_current, na.rm = TRUE))) +
  facet_wrap(~case_status) +
  labs(title = 'Current Weight Suppression based on Diagnosis History and History or of DEx', x = 'History of Driven Exercise', y = 'Median Weight Suppression - Current') +
  theme(legend.position = 'none') +
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) +
  geom_text(data = medians, aes(x = ED100k_exercise_icb_factor, y = median_ws_high_current+5, label = round(median_ws_high_current, 1)), size = 3, color = 'black', fontface ='bold') + 
  coord_cartesian(ylim  = c( 0,  80))

    
ws_plot

```

```{r}
wt_variablility_plot <- ggplot (EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = ED100k_wt_suppress_high_low, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color =  'black', aes(middle = median(ED100k_wt_suppress_high_low, na.rm = TRUE))) +
  facet_wrap(~case_status) +
  labs(title = 'Weight variability (difference in highest vs lowest weight) based on Diagnosis Hx and Hx or of DEx', x = 'History of Driven Exercise', y = 'Median Weight Suppression - Current') +
  theme(legend.position = 'none') +
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) +
  geom_text(data = medians, aes(x = ED100k_exercise_icb_factor, y = median_ws_high_low + 10, label = round(median_ws_high_low, 1)), size = 3, color = 'black', fontface ='bold') + 
  coord_cartesian(ylim  = c( 0,  200))

    
wt_variablility_plot

```

```{r}
wt_restore_plot <- ggplot (EDGI_exercise_cleaned, aes(x = ED100k_exercise_icb_factor, y = ED100k_wt_suppress_curr_low, color = ED100k_exercise_icb_factor)) + 
  geom_jitter(size = 0.3) +
  scale_color_manual(values = c('purple', 'blue', 'orange')) +
  geom_boxplot(alpha = 0.5, color =  'black', aes(middle = median(ED100k_wt_suppress_curr_low, na.rm = TRUE))) +
  facet_wrap(~case_status) +
  labs(title = 'Weight restoration (difference between lowest and current weight) based on Diagnosis History and History or of DEx', x = 'History of Driven Exercise', y = 'Current - Lowest Weight') +
  theme(legend.position = 'none') +
  scale_x_discrete(labels = c('Never', 'A Few', 'More Often')) +
  geom_text(data = medians, aes(x = ED100k_exercise_icb_factor, y = median_ws_curr_low + 10, label = round(median_ws_curr_low, 1)), size = 3, color = 'black', fontface ='bold') + 
  coord_cartesian(ylim  = c( 0,  200))

    
wt_restore_plot


```



