---
title: "Scoring for EDGI Exercise"
author: "Katherine Schaumberg"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}
#Loads packages
library(scorekeeper)
library(sjmisc)
library(haven)
library(dplyr)
library(tidyr)
library(readxl)
library(cgwtools)
library(expss)
```


```{r, results='hide', echo=FALSE}
## loads raw data and scoresheets. data needs to be loaded into data/ folder prior to running below

EDGI_raw <- read_sas('data/exercise.sas7bdat') 
ED100k_score <- read_excel("EDGI_exercise_scoresheet.xlsx", 'ED100k')
EDEQ_score <- read_excel("EDGI_exercise_scoresheet.xlsx", 'EDEQ')
CET_score <- read_excel("EDGI_exercise_scoresheet.xlsx", 'CET')

```

# ED100k

## Background 

ED100K.V3 questionnaire is a self-report, ED assessment based on the Structured Clinical Interview for DSM-5, Eating Disorders. Items assess DSM-5 criteria for AN, BN, BED, and other specified feeding and eating disorders (OSFED). The ED100K-V1 was found to be a valid measure of eating disorders and eating disorder behaviors. Positive predictive values for AN Criterion B, Criterion C, and binge eating ranged from 88 to 100%. Among women who had a negative screen, the probability of not having these criteria or behaviors ranged from 72 to 100%. The correlation between questionnaire and interview for lowest illness-related BMI was 0.91. Captures: diagnosis, symptoms, course of illness, diagnostic fluctuation.

**Key Citation**

Thornton L, Munn-Chernoff M, Baker J, Juréus A, Parker R, Henders A, et al. The anorexia nervosa genetics initiative (ANGI): overview and methods. Contemp Clin Trials. 2018;74:61–9. https://doi.org/10.1016/j.cct.2018.09.015.


## Scoring

Of note, the ED100k primarily captures *historical* engagement in maladaptive exercise beahviors, while the CET and EDEQ (detailed below) are focused primarily on current maladaptive exercise behavior. In addition to exercise variables, age of onset, duration, most recent age of engagement, and current engagement variables for other eating disorder behaviors (vomiting, laxative use, diet pills, diuretics, binge eating, and fasting) are included in scoring.

**Step 1** selects variables to be used in the current analysis.

**Step 2** recodes the compensatory exercise variable to remove missing codes, and recodes intentional weight control variables to remove missing codes and set '0' equal to a 'No/Never' answer

**Step 3** overrides skip logic for exercise and other weight control variables such that if individuals have an initial 'no' answer where skip logic has overridden future questions, a '0' (reflecting a 'no/never' answer) is entered in the subsequent question regarding details of the behavior. 

**Step 4** is a second recode for these questions such that missing codes are  change to 'NA' and the '0' answers are labelled appropriately

**Steps 5-7** specifically calculate logic necessary to specify exercise-related outcome variables, described in key variables below.

**Step 8** cleans up the dataset by removing erroneous variables that are no longer needed. 

After these steps ar complete,  additional weight suppression variables are calculated and added to the data

## Key varaiables
Key variables relevant for the current papers include:

**Demographic Variables**

`ED100k_ethnicity_dummy_1` (Race dummy coded Non-Hispanic White vs All other)

`ED100k_ethnicity_dummy_2` (Race dummy coded White, Black, Asian/PI, Hispanic (non-black), Other)

`age` (age at time of assessment)

**Exercise Variables**

`ED100k_exercise_icb` (Was exercise ever used as a behavior to intentionally control weight or shape?)

`ED100k_ex_compulsive` (Ever felt compelled to exercise for wt and shape control OR uneasy / distressed if unable to exercise)

`ED100k_ex_interfere` (Did exercise ever interfere in one's life (changing eating habits, declining opportunities to be with friends, exercising despite illness or injury)

`ED100k_ex_interfere_sum_complete` (Sum of criterion (max = 3) for exercise interference items)

`ED100k_ex_excessive` (>1 month of psychologically driven exercise every day or nearly every day)

`ED100k_ex_addictive` (Having psychologically compulsive/driven exercise (feeling compelled to exercise or distressed if unable) that lasted for at least one month AND at least one life interfering symptom)

`ED100k_ex_compulsive_1mo` (Compulsive/Driven Exercise that lasted for at least one month)

`ED100k_ex_maladaptive_1mo` (reports driven exercise for at least one month OR any compensatory exercise)

`ED100k_ex_dur` (For how long did you feel compelled to exercise or felt distressed if unable to exercise?)

`ED100k_ex_freq` (During these periods, how frequently did you exercise excessively in a week?)

`ex_age_last` (How old were you when you stopped exercising to control your weight and shape AND felt either compelled to exercise or distressed if unable to exercise?)

`ex_age` (How old were you when you first exercised to control your weight and shape AND felt either compelled to exercise or distressed if unable to exercise?)

`ex_current` (Do you currently exercise to control weight and shape AND feel compelled to exercise or distress if unable to exercise?)

**Case Status Variables**

`an_case`, `bn_case`, `bed_case`, `control` - P re-derived variables identifying cases and controls
 
**Weight suppression variables**

`ED100k_wt_suppress_high_current` - current weight suppression 

`ED100k_wt_suppress_high_lowest` - difference between highest weight and lowest weight at adult height

`ED100k_wt_suppress_high_AN` - difference between highest ever weight at adult height and weight during an AN episode

`ED100k_wt_suppress_current_AN` - difference between current weight and weight duirng an AN episode 

`ED100k_bmi_suppress_high_current`, `ED100k_bmi_suppress_high_lowest`, `ED100k_bmi_suppress_high_AN`, `ED100k_bmi_suppress_current_AN` - BMI versions of above variables

```{r, warning=FALSE, echo=FALSE}

ED100k<- scorekeep(EDGI_raw, ED100k_score)
ED100k_scored <- ED100k [[8]]

# Add various weight suppression variables; clean outlier BMI variables
ED100k_scored <- ED100k_scored |> 
  mutate (highestbmi = round(703*wt_hi_lb/(height^2), 2))  |> 
  mutate (lowestbmi = round(703*wt_lo_lb/(height^2), 2)) |>
  mutate( ED100k_wt_suppress_high_current = wt_hi_lb - wt_cur_lb) |> 
  mutate( ED100k_wt_suppress_high_AN = wt_hi_lb - wt_loan_lb) |> 
  mutate( ED100k_wt_suppress_current_AN = wt_cur_lb - wt_loan_lb) |> 
  mutate( ED100k_wt_suppress_high_low = wt_hi_lb - wt_lo_lb) |> 
  mutate( ED100k_wt_suppress_curr_low = wt_cur_lb - wt_lo_lb) |> 
  mutate( ED100k_bmi_suppress_high_curr = highestbmi -  currentbmi) |> 
  mutate( ED100k_bmi_suppress_high_low = highestbmi- lowestbmi) |> 
  mutate( ED100k_bmi_suppress_high_AN = round(703*wt_hi_lb/(height^2),2) - an_bmi) |> 
  mutate( ED100k_bmi_suppress_current_AN = currentbmi - an_bmi) |> 
  mutate( ED100k_bmi_suppress_current_low = currentbmi - lowestbmi) 

save (ED100k_scored, file = "data/EDGI_scored_data.RData")
```

# EDEQ

## Background 
The EDEQ was created by Fairburn and Beglin 1994. It has been well-validated in both clinical and community samples. Correlations between EDE-Q and EDE subscales ranged from 0.68 for Eating Concern to 0.78 for Shape Concern (Mond, 2004)

## Scoring 
The EDE, and its self-report version, the EDE-Q, generate two types of data. First, they provide frequency data on key behavioural features of eating disorders in terms of number of episodes of the Behaviour and in some instances number of days on which the behaviour has occurred. Second, they provide subscale scores reflecting the severity of aspects of the psychopathology of eating disorders.

The subscales are Restraint, Eating Concern, Shape Concern and Weight Concern. To obtain a particular subscale score, the ratings for the relevant items are added together and the sum divided by the total number of items forming the subscale (subscale scores are mean scores). For the purposes of current scoring, subscale scores are derived 75% or greater of items are answered in a particular subscale. 

Scoring is completed as follows: 

**Step 1** Selects all EDEQ raw variables

**Step 2** Mean subscale scores derived for four subscales

**Step 3** Behavioral variables renamed to indicate that they are assessing each specific behavior

**Step 4** Subscale scores retained only for those with 25% missing data on each subscale

**Step 5** EDEQ Global scale computed from the mean of subscale scores

## Key Variables
`edeq_restraint` (dietary restraint subscale of the EDEQ)

`edeq_ec`(eating concerns subscale of the EDEQ)

`edeq_sc` (shape concerns subscale of the EDEQ)

`edeq_wc` (weight concerns subscale of the EDEQ)

`edeq_loc_freq_28`  (loss of control frequency in the past 28 days)

`edeq_binge_days_28` (number of days with objective binge eating in the past 28 days)

`edeq_vomit_freq_28` (number of times vomitted in past 28 days for weight/shape control)

`edeq_laxative_freq_28` (number of times of laxative use in past 28 days for weight/shape control)

`edeq_ex_driven_freq_28` (number of times driven exercise in past 28 days for weight/shape control)

`edeq_fast_freq_28_ordinal` (ordinal response to number of days engaged in fasting in past 28 for weight/shape control) 

`edeq_global_complete` (EDEQ global scale - those with valid subscale data on all 4 subscales only)


```{r, echo=FALSE}
EDEQ_scored <- scorekeep(EDGI_raw, EDEQ_score)
EDEQ_scored <- EDEQ_scored [[5]]
resave (EDEQ_scored, file = "data/EDGI_scored_data.RData")

```


# CET 

## Background 
The CET is the first measure of problematic exercise that has been developed specifically for use in eating disorders research and assessment, and within a cognitive-behavioural framework. The following references are the key publications:

1. Taranis, L., Touyz, S., & Meyer, C. (2011). Disordered eating and exercise: Development and preliminary validation of the Compulsive Exercise Test (CET.) European Eating Disorders Review, 19, 256-268
2. Goodwin, H., Haycraft, E., Taranis, L. & Meyer, C. (2011). Psychometric evaluation of the Compulsive Exercise Test (CET) in an adolescent population: Links with eating psychopathology. European Eating Disorders Review.19, 269-279.
3. Meyer, C., Taranis, L., Goodwin, H., & Haycraft, E. (2011). Compulsive exercise and eating disorders. European Eating Disorders Review, 19 174-189.

The CET is a 24-item self-report measure designed to assess the core features of excessive exercise in
the eating disorders; compulsivity (e.g. continuing to exercise despite illness or injury, lack of exercise enjoyment, the experience of extreme guilt when unable to exercise, making up for missed exercise sessions), affect regulation (e.g. the positive and negative reinforcement properties of exercise), weight and shape driven exercise (e.g. exercising solely to burn calories, compensatory exercise such as debting), and exercise rigidity (rigid adherence to a strict and repetitive exercise routine). Items were generated from a comprehensive appraisal of the eating disorder and excessive exercise literature, consultation with clinical eating disorder specialists, interviews with eating disorder patients, and a critical review of existing scales, and were included based on theoretical relevance and clinical specificity.

The CET uses a 6-point Likert scale anchored by 0 (never true) and 5 (always true) with higher scores indicative of greater pathology. Factor analysis revealed 5 factors explaining 63.5% of the variance. These were used to construct the 5 subscales of: avoidance and rule-driven behaviour, weight control exercise, mood improvement, lack of exercise enjoyment, and exercise rigidity. Initial validation results are encouraging with good internal consistency, content validity, and concurrent validity of the CET. The CET also demonstrates strong positive associations with measures of eating pathology and known correlates of disordered eating. It is concluded that the CET could be a reliable and valid instrument for use in both clinical and research settings.

## Scoring 

 **Step 1** - Selects the CET variables
 
 **Step 2** - Items are renamed so that the item content is quickly visible in the item name and items 8 and 12 are reverse scored. 
 
 **Step 3** - Calculates subscale scores by taking the mean scores of each subscale
 
 **Step 4** - Creates subscale variables recoding to NA for individuals with  > 25% missing on a subscale
 
 **Step 5**  - Creates the total score by summing the subscale scores
 
 **Step 6** - Identifies individuals scoring at or above the clinical cutoff (15) on the total score
 
 **Step 7** - Reselects variables for inclusion in final dataset
 
## Key Variables 

Key variables calculated from the current scoring include: 

`cet_avoid` (CET avoidance and rule-driven behavior subscale -- < 25% missing) 

`cet_wtcontrol` (CET weight control exercise subscale -- < 25% missing) 

`cet_mood` (CET mood improvement subscale -- < 25% missing)

`cet_enjoy` (CET lack of exercise enjoyment subscale -- < 25% missing)

`cet_rigid` (CET exercise rigidity subscale -- < 25% missing)

`cet_total_complete` (CET total score - valid subscale data on all subscales)

`cet_clinical` (Clinical cutoff score of 15 - using weighted Sum)


```{r, warning = FALSE, echo = FALSE}

CET_scored <- scorekeep(EDGI_raw, CET_score)
CET_scored <- CET_scored [[6]]
resave (CET_scored, file = "data/EDGI_scored_data.RData")

```

```{r warning = FALSE, echo=FALSE}
load('data/EDGI_scored_data.RData')

Data <- full_join(CET_scored,ED100k_scored)
EDGI_exercise_cleaned <- full_join(Data, EDEQ_scored) |> 
  mutate (ex_age = na_if(ex_age, 233)) |> 
  rename_all(function(x) gsub('.factor', '_factor', x)) |> 
  rename(ED100k_ex_int_sumNA = ED100k_ex_interfere_sum_NA_percent) |> #renames to shorter for SAS friendly variable name
  rename(ED100k_ex_int_weightedsum = ED100k_ex_interfere_sum_weighted_sum) #renames to shorter for SAS friendly variable name
write_sas(EDGI_exercise_cleaned, 'data/exercise_cleaned.sas7bdat')
save(EDGI_exercise_cleaned, file = "data/EDGI_exercise_cleaned.RData")
```




