
---
title: EDGI Exercise Validation Paper Results
author: Katherine Schaumberg
output:
  bookdown::html_document2: default
---

```{r, setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE,  warning = FALSE)
library(expss)
library(bookdown)
library(dplyr)
library(haven)
library(sjmisc)
library(rmarkdown)
library(knitr)
library(psych)
library(ggplot2)
load('data/EDGI_exercise_cleaned.RData') 

exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_exercise_icb > 0)
regular_exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_exercise_icb == 2)
compulsive_exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_ex_compulsive >0)
regular_compulsive_exercisers <- EDGI_exercise_cleaned |> 
  filter (ED100k_ex_compulsive_strict == 1)

```


### Compulsive Exercise

Only those who endorsed EVER Exercising to intentionally control weight
or shape were asked to report (Yes/No) the next two questions - whether
they felt compelled to exercise (`ex_compel`) or whether they felt
distress if unable to exercise (`ex_distress`). In re-coding, those (n =
945) who reported no no exercise to control shape and weight were marked
as 0 for these two questions. These two questions were then combined
using OR logic to determine compulsive exercise - with individuals being
classified as compulsive exercisers if they reported either feeling
compelled to exercise or distress if unable to exercise.

`ED100k_ex_compulsive` (Ever felt compelled to exercise for wt and shape
control OR uneasy / distressed if unable to exercise)

`ED100k_ex_compulsive_strict` (Report exercising for weight loss 'more often' AND felt compelled to exercise or uneasy/distressed if unable to exercise)

```{r, echo=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive_strict)

frq(EDGI_exercise_cleaned$ED100k_ex_compulsive)
```

Amongst those who reported ANY exercise for shape and weight control and
were asked explicitly about compulsive exercise (not skipped), rates of
endorsement for either feeling compelled to exercise OR feeling distressed when unable to exercise are hight (96%); among those who reported exercise for shape and weight control 'more often', endorsement of either feeling compelled to exercise OR feeling distressed when unable to exercise is 99.5% -- indicating that these two questions be unnecessary for defining compulsive exercise *within* eating disordered samples, or that non-binary responses may elucidate degree of these 

Those who reported any compulsive exercise were further asked a series
of questions, including how long they felt compelled to exercise or
distressed when unable to exercise. In addition to the 24 individuals
who did not report on compulsion/distress, 217 additional individuals
did not report duration. Those who reported No Exercise for Weight
Control OR No Compulsive Exercise were coded as '0' for this item.

`ED100k_ex_dur` (For how long did you feel compelled to exercise or felt
distressed if unable to exercise?)

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_dur)
```



`ED100k_ex_compulsive_1mo`  categorizes whether compulsive exercise was present for at least one month, while `ED100k_ex_compulsive_strict_3mo` categorizes whether compulsive exercise lasted for at least three months and exercise was endorsed 'more often' as a weight control behavior. Once again, the vast majority of individuals (98.2%) who endorsed exercising 'more often' met criteria for compulsive exercise that lasted at least 3 months in duration, suggesting that those with eating disorders who endorse using exercise to intentionally control weight 'more often' are doing so for a substantive period of time. 



```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive_1mo)
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive_strict_3mo)

frq(regular_exercisers$ED100k_ex_compulsive_strict_3mo)
```




#### Age of Onset and Age of Last Reported Compulsive Exercise 

Age of last reported compulsive exercise was captured for those reporting compulsive exercise: 

`ex_age_last` (How old were you when you stopped exercising to control your weight and shape AND felt either compelled to exercise or distressed if unable to exercise?)

Mean age of last exercise = `r mean(EDGI_exercise_cleaned$ex_age_last, na.rm = TRUE)` SD = `r sd(EDGI_exercise_cleaned$ex_age_last, na.rm = TRUE)` 

About half of the sample reporting regular ('more often') compulsive exercise (total n = `r nrow(regular_compulsive_exercisers)` did not report age of last compulsive exercise (n not reporting = `r sum(is.na(regular_compulsive_exercisers$ex_age_last))`), in line with the finding that many individuals were currently experiencing the symptom (below)


```{r}
hist(regular_compulsive_exercisers$ex_age_last)
```

Individuals reporting a history of regular compulsive exercise were also asked when the first time they experienced this symptom. 

`ex_age` (How old were you when you first exercised to control your weight and shape AND felt either compelled to exercise or distressed if unable to exercise?)

One participant reported age of onset as '233', which was removed as NA before analysis.

```{r}
hist(regular_compulsive_exercisers$ex_age)
```


Mean age of first exercise = `r mean(regular_compulsive_exercisers$ex_age, na.rm = TRUE)` SD = `r sd(regular_compulsive_exercisers$ex_age, na.rm = TRUE)` 

All participants reporting regular compulsive exercise (total n = `r nrow(regular_compulsive_exercisers)` reported  age of onset.


```{r}
range(regular_compulsive_exercisers$ex_age, na.rm = TRUE)
```


#### Current Compulsive Exercise

In addition to history of compulsive exercise, individuals who endorsed history of compulsive exercise were asked if they currently engage in exercise to control weight and shape AND feel compelled to exercise or distress if unable to exercise (`ex_current`), which was recoded to impute 0 values for those with no history of compulsive exercise (ED100k_ex_compulsive_current). About 40% of the TOTAL sample (valid n = 7235) reported compulsive exercise was an ongoing symptom.

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive_current)
```

Among those reporting history of regular compulsive exercise, over half of participants reported current compulsive exercise

```{r, echo=FALSE,message=FALSE}
frq(regular_compulsive_exercisers$ED100k_ex_compulsive_current)
```

### Exercise Addiction

We defined exercise addiction as having regular compulsive exercise for at least three months AND having exercise interfere with one's life. 

Individuals any compulsive exercise were also asked whether this interfered with their life in a series of 3 questions -- whether it caused them to change eating habits, decline opportunities to be with friends, or whether they exercised despite illness or injury. 

The full sample results are presented below (imputed to be 'no' for those who reported no compulsive exercise). Individuals reporting YES to ANY of those three symptoms were coded YES in response to Exercise Interference

`ED100k_ex_interfere` (Did exercise ever interfere in one's life (changing eating habits, declining opportunities to be with friends, exercising despite illness or injury) 
```{r, echo=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_interfere)
```

When looking at just those with regular ('more often') exercise, rates of endorsement were 98%, again indicating that the vast majority of indivdiuals reporting regular exercise for weight loss to control weight and shape also experienced life interfering sequellae of this behavior. 

```{r}

frq(regular_exercisers$ED100k_ex_interfere)
```

In the entire sample, the modal number of exercise interference items was all 3

`ED100k_ex_interfere_sum_complete` (Sum of criterion (max = 3) for exercise interference items) 
```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_interfere_sum_complete
    )
```

And examining only those who reported regular ('more often') exercise, the majority reported all three life interference items

```{r}

frq(regular_exercisers$ED100k_ex_interfere_sum_complete)
```

The following variable defines presence of addictive exercise in the whole sample:

`ED100k_ex_addictive` (Regular exercise for weight control and feeling compelled to exercise or distressed if unable to exercise that lasted for at least 3 months AND at least one life interfering symptom

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_addictive)
```


### Excessive Exercise 

Excessive exercise was defined as compulsive exercise occurring for at least one month, every day or nearly ever day. Among the whole sample ('0' imputed for those reported no compulsive exercise), rates are:  

`ED100k_ex_excessive` (>1 month of compulsive exercise every day or nearly every day) 
```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_excessive)
```


Among the subsample who reported regular compulsive exercise, rates are about 80% reporting at least one month of compulsive exercise every day or nearly every day.

```{r, echo=FALSE,message=FALSE}
frq(regular_compulsive_exercisers$ED100k_ex_excessive)
```


### Compensatory Exercise

All participants were asked about compensatory exercise (`be_icb__5`), with about half of the sample reporting compensatory exercise: 

```{r}
frq(EDGI_exercise_cleaned$be_icb___5)
```

Among those with regular exercise, rates were somehwat higher (>60%), 


```{r}
frq(regular_exercisers$be_icb___5)
```

### Broad Maladaptive Exercise

A broad maladaptive exercise variable was the final exercise variable made, which included individuals who reported regular exercise for weight loss ('more often') with at 3 months of compulsive exercise OR any compensatory exercise

In the full sampple, xxx % met criteria

Among those reporting regular exercise, xxx% met criteria

`ED100k_ex_maladaptive` (reports 3 months of compensatory exercise OR any compensatory exercise)  

Overall, there 
```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_maladaptive)
```

When examining overlap in compensatory and compulsive exercise, the vast majority of individuals endorsing compensatory exercise 
```{r}
ct <- table(EDGI_exercise_cleaned$ED100k_ex_compulsive, EDGI_exercise_cleaned$ED100k_ex_compensatory)

ex_row_percents <- prop.table (ct, 1)

ex_row_percents <- as.data.frame(ex_row_percents) |> 
 rename(`Compulsive Exercise` = Var1) |> 
 rename(`Compensatory Exercise` = Var2) |> 
filter(`Compensatory Exercise` == 1)

ggplot(ex_row_percents, aes( x = `Compulsive Exercise`, y = Freq*100, fill = `Compensatory Exercise` )) + 
  geom_col()+
  labs(title = 'Compensatory vs. Compulsive Exercise', x = 'Compulsive Exercise', y = 'Percent Endorsing Compensatory Exercise') + 
  scale_x_discrete(labels = c('No', 'Yes')) +
      theme(legend.position = 'none') 


```

