---
title: EDGI Exercise Validation Paper Results
author: Katherine Schaumberg
output:
  bookdown::html_document2: default
editor_options: 
  markdown: 
---

```{r, setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE,  warning = FALSE)
library(expss)
library(bookdown)
library(dplyr)
library(haven)
library(sjmisc)
library(rmarkdown)
library(knitr)
library(psych)
library(ggplot2)
load('data/EDGI_exercise_cleaned.RData') 

exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_exercise_icb > 0)
regular_exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_exercise_icb == 2)
compulsive_exercisers <- EDGI_exercise_cleaned |> 
  filter(ED100k_ex_compulsive >0)
regular_compulsive_exercisers <- EDGI_exercise_cleaned |> 
  filter (ED100k_ex_compulsive_strict == 1)

```

# Compulsive Exercise

Only those who endorsed EVER Exercising to intentionally control weight
or shape were asked to report (Yes/No) the next two questions - whether
they felt compelled to exercise (`ex_compel`) or whether they felt
distress if unable to exercise (`ex_distress`). In re-coding, those (n =
945) who reported no no exercise to control shape and weight were marked
as 0 for these two questions. These two questions were then combined
using OR logic to determine compulsive exercise - with individuals being
classified as *ever compulsive exercisers* if they reported exercising
to intentionally control wieght and shape at all and either feeling
compelled to exercise or distress if unable to exercise for any amount
of time.

```{r, echo=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive)

```

Amongst those who reported ANY exercise for shape and weight control and
were asked explicitly about compulsive exercise (not skipped), rates of
endorsement for either feeling compelled to exercise OR feeling
distressed when unable to exercise are hight (96%); among those who
reported exercise for shape and weight control 'more often', endorsement
of either feeling compelled to exercise OR feeling distressed when
unable to exercise is 99.5% -- indicating that these two questions be
unnecessary for defining compulsive exercise *within* eating disordered
samples, or that non-binary responses may elucidate degree of these

Those who reported either compelled to exercise or distressed when
unable to exercise were further asked how long they felt this way. In
addition to the 24 individuals who did not report on
compulsion/distress, 217 additional individuals did not report duration.
Those who reported No Compulsive Exercise symptoms were coded as '0' for
this item.


```{r}
frq(EDGI_exercise_cleaned$ED100k_ex_dur)
```
We then defined regular compulsive exercisers as those who endorsed
using exercise as a weight control behavior 'more often' and reported
either compulsive exercise symptom which lasted for at least three
months in duration.

The vast majority of individuals who endorsed exercising 'more often' in
the first question of the series reported either feeling compelled to
exercise and/or distressed when unable to exercise for a period that
lasted at least 3 months in duration
`r frq(regular_exercisers$ED100k_ex_compulsive_strict_3mo)`,
highlighting convergent validity of the first and third questions and
suggesting that those with eating disorders who endorse using exercise
to intentionally control weight 'more often' are doing so for a
substantive period of time.

## Age of Onset and Age of Last Reported Compulsive Exercise

Age of last reported compulsive exercise was captured for the ever
compulsive exercise group (any duration):

Mean age of last exercise =
`r mean(EDGI_exercise_cleaned$ex_age_last, na.rm = TRUE)` SD =
`r sd(EDGI_exercise_cleaned$ex_age_last, na.rm = TRUE)`

About half of the sample reporting regular compulsive exercise (total n
= `r nrow(regular_compulsive_exercisers)` did not report age of last
compulsive exercise (n not reporting =
`r sum(is.na(regular_compulsive_exercisers$ex_age_last))`), which
suggests (as mentioned below) that many individuals were currently
experiencing the symptom.

Individuals reporting a history of compulsive exercise were also asked
when the first time they experienced this symptom.

One participant reported age of onset as '233', which was removed as NA
before analysis. Median age of first exercise is
`r median(regular_compulsive_exercisers$ex_age, na.rm = TRUE)`, with
range = `r range(regular_compulsive_exercisers$ex_age, na.rm = TRUE)`
among those who reported regular compulsive exercise, with all
participants reporting regular compulsive exercise reporting age of
onset

## Current Compulsive Exercise

In addition to history of compulsive exercise, individuals who endorsed
history of compulsive exercise were asked if they currently engage in
exercise to control weight and shape AND feel compelled to exercise or
distress if unable to exercise (`ex_current`), which was recoded to
impute 0 values for those with no history of compulsive exercise
(ED100k_ex_compulsive_current). About 40% of the TOTAL sample (valid n =
7235) reported compulsive exercise was an ongoing symptom.

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive_current)
```

Among those reporting history of regular compulsive exercise, over half
of participants reported current compulsive exercise

```{r, echo=FALSE,message=FALSE}
frq(regular_compulsive_exercisers$ED100k_ex_compulsive_current)
```

# Exercise Addiction

We defined exercise addiction as having regular compulsvie exercise for
at least three months AND having exercise interfere with one's life.
Individuals with any compulsive exercise symptoms were also asked
whether this interfered with their life in a series of 3 questions --
whether it caused them to change eating habits, decline opportunities to
be with friends, or whether they exercised despite illness or injury.

The full sample results are presented below (imputed to be 'no' for
those who reported no compulsive exercise symptoms). Individuals
reporting YES to ANY of those three symptoms were coded YES in response
to Exercise Interference.

```{r, echo=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_interfere)
```

When looking at just those with regular exercise for weight control,
rates of endorsement of life interfering symptoms were 98%, again
indicating that the vast majority of indivdiuals reporting regular
exercise for weight loss to control weight and shape also experienced
life interfering sequellae of this behavior.

```{r}
frq(regular_exercisers$ED100k_ex_interfere)
```

In the entire sample as well as those with regular exercise for weight
control, the modal number of exercise interference items was all 3. \`

The following variable defines presence of addictive exercise in the
whole sample:

`ED100k_ex_addictive` (Regular exercise for weight control and feeling
compelled to exercise or distressed if unable to exercise that lasted
for at least 3 months AND at least one life interfering symptom

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_addictive)
```

# Excessive Exercise

Excessive exercise was defined as compulsive exercise occurring for at
least one month, every day or nearly ever day. Among the whole sample
('0' imputed for those reported no compulsive exercise), rates are:

`ED100k_ex_excessive` (\>1 month of compulsive exercise every day or
nearly every day)

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_excessive)
```

Among the subsample who reported regular compulsive exercise, rates are
about 80% reporting at least one month of compulsive exercise every day
or nearly every day.

```{r, echo=FALSE,message=FALSE}
frq(regular_compulsive_exercisers$ED100k_ex_excessive)
```

# Compensatory Exercise

All participants were asked about compensatory exercise (`be_icb__5`),
with about half of the sample reporting compensatory exercise:

```{r}
frq(EDGI_exercise_cleaned$be_icb___5)
```

Among those with regular exercise, rates were somehwat higher (\>60%),

```{r}
frq(regular_exercisers$be_icb___5)
```

# Broad Maladaptive Exercise

A broad maladaptive exercise variable was the final exercise variable
made, which included individuals who reported regular exercise for
weight loss ('more often') for at 3 months with compulsive symptoms OR
any compensatory exercise

In the full sampple, xxx % met criteria

Among those reporting regular exercise, xxx% met criteria

`ED100k_ex_maladaptive` (reports 3 months of compensatory exercise OR
any compensatory exercise)

Overall, there

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_maladaptive)

frq(regular_exercisers$ED100k_ex_maladaptive)

```

When examining overlap in compensatory and compulsive exercise, the vast
majority of individuals endorsing compensatory exercise

```{r}
ct <- table(EDGI_exercise_cleaned$ED100k_ex_compulsive, EDGI_exercise_cleaned$ED100k_ex_compensatory)

ex_row_percents <- prop.table (ct, 1)

ex_row_percents <- as.data.frame(ex_row_percents) |> 
 rename(`Compulsive Exercise` = Var1) |> 
 rename(`Compensatory Exercise` = Var2) |> 
filter(`Compensatory Exercise` == 1)

ggplot(ex_row_percents, aes( x = `Compulsive Exercise`, y = Freq*100, fill = `Compensatory Exercise` )) + 
  geom_col()+
  labs(title = 'Compensatory vs. Compulsive Exercise', x = 'Compulsive Exercise', y = 'Percent Endorsing Compensatory Exercise') + 
  scale_x_discrete(labels = c('No', 'Yes')) +
      theme(legend.position = 'none') 


```

2.  Examine convergent validity: [zero-order correlations]

<!-- -->

a.  Current Exercise
b.  Frequency of driven exercise over the past 28 days -- EDE-Q item 18

<!-- -->

ii. CET total and subscale mean ± SD scores
iii. CET clinical cutoff (prevalence: frequency and 95% CI calculated
     with the binomial distribution)

<!-- -->

b.  Perfectionism
c.  OCD symtpoms

<!-- -->

3.  Examine discriminant validity:

<!-- -->

a.  OCD symptoms

<!-- -->

4.  Examine prevalence of differing constructs

<!-- -->

a.  In overall sample
b.  Among diagnostic groups

<!-- -->

5.  Examine associations with illness history, other symptoms
    [correlations]
