### Compulsive Exercise

Only those who endorsed EVER Exercising to intentionally control weight
or shape were asked to report (Yes/No) the next two questions - whether
they felt compelled to exercise (`ex_compel`) or whether they felt
distress if unable to exercise (`ex_distress`). In re-coding, those (n =
945) who reported no no exercise to control shape and weight were marked
as 0 for these two questions. These two questions were then combined
using OR logic to determine compulsive exercise - with individuals being
classified as compulsive exercisers if they reported either feeling
compelled to exercise or distress if unable to exercise.

`ED100k_ex_compulsive` (Ever felt compelled to exercise for wt and shape
control OR uneasy / distressed if unable to exercise)

```{r, echo=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive)
```

Amongst those who reported ANY exercise for shape and weight control and
were asked explicitly about compulsive exercise (not skipped), rates of
endorsement for compulsive exercise are high (96%):

```{r}

frq(exercisers$ED100k_ex_compulsive)
```

Those who reported any compulsive exercise were further asked a series
of questions, including how long they felt compelled to exercise or
distressed when unable to exercise. In addition to the 24 individuals
who did not report on compulsion/distress, 217 additional individuals
did not report duration. Those who reported No Exercise for Weight
Control OR No Compulsive Exercise were coded as '0' for this item.

`ED100k_ex_dur` (For how long did you feel compelled to exercise or felt
distressed if unable to exercise?)

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_dur)
```

The following categorizes whether compulsive exercise was present for at
least one month

`ED100k_ex_compulsive_1mo` (Compulsive/Driven Exercise that lasted for
at least one month)

```{r, echo=FALSE,message=FALSE}
frq(EDGI_exercise_cleaned$ED100k_ex_compulsive_1mo)
```

#### Age of Onset and Age of Last Reported Compulsive Exercise 

Age of last reported compulsive exercise was captured for those reporting compulsive exercise: 

`ex_age_last` (How old were you when you stopped exercising to control your weight and shape AND felt either compelled to exercise or distressed if unable to exercise?)

Mean age of last exercise = `r mean(full_data$ex_age_last, na.rm = TRUE)` SD = `r sd(full_data$ex_age_last, na.rm = TRUE)` 

About half of the sample (total n = `r nrow(compulsive_exercisers)` did not report age of last compulsive exercise (n not reporting = `r sum(is.na(compulsive_exercisers$ex_age_last))`), in line with the finding that many individuals were currently experiencing the symptom (below)


```{r}
hist(compulsive_exercisers$ex_age_last)
```

Individuals reporting compulsive Exercise history were also asked when the first time they experienced this symptom. 

`ex_age` (How old were you when you first exercised to control your weight and shape AND felt either compelled to exercise or distressed if unable to exercise?)

One participant reported age of onset as '233', which was removed as NA before analysis.

```{r}
hist(compulsive_exercisers$ex_age)
```


Mean age of first exercise = `r mean(compulsive_exercisers$ex_age, na.rm = TRUE)` SD = `r sd(compulsive_exercisers$ex_age, na.rm = TRUE)` 

All participants reporting compulsive exercise (total n = `r nrow(compulsive_exercisers)` reported  age of onset, with the exception of the out of range value identified (n not reporting = `r sum(is.na(compulsive_exercisers$ex_age))`)


```{r}
range(compulsive_exercisers$ex_age, na.rm = TRUE)
```



#### Current Compulsive Exercise

•	C
In addition to history of compulsive exercise, individuals who endorsed history of compulsive exercise were asked if they currently engage in exercise to control weight and shape AND feel compelled to exercise or distress if unable to exercise (`ex_current`), which was recoded to impute 0 values for those with no history of compulsive exercise (ED100k_ex_compulsive_current). About 40% of the sample reported current compulsive exercise in the ED100k

```{r, echo=FALSE,message=FALSE}
frq(full_data$ED100k_ex_compulsive_current)
```


Among those reporting history of compulsive exercise, rates were: 

```{r, echo=FALSE,message=FALSE}
frq(compulsive_exercisers$ED100k_ex_compulsive_current)
```

### Exercise Addiction

We defined exercise addiction as having compulsive exercise for at least one month AND having exercise interfere with one's life. 

Individuals reporting any compulsive exercise were also asked whether this interfered with their life in a series of 3 questions -- whether it caused them to change eating habits, decline opportunities to be with friends, or whether they exercised despite illness or injury. The full sample results are presented below (imputed to be 'no' for those who reported no compulsive exercise). Individuals reporting YES to ANY of those three symptoms were coded YES in response to Exercise Interference


`ED100k_ex_interfere` (Did exercise ever interfere in one's life (changing eating habits, declining opportunities to be with friends, exercising despite illness or injury) 
```{r, echo=FALSE}
frq(full_data$ED100k_ex_interfere)
```

When looking at just those who were explicitly asked questions about whether exercise interfered with one's life (those reporting compulsive exercise), rates of endorsement were high. 

```{r}

frq(exercisers$ED100k_ex_interfere)
```

In the entire sample, the modal number of exercise interference items was all 3

`ED100k_ex_interfere_sum_complete` (Sum of criterion (max = 3) for exercise interference items) 
```{r, echo=FALSE,message=FALSE}
frq(full_data$ED100k_ex_interfere_sum_complete
    )
```

And examining only those who reported compulsive exercise, the majority reported all three life interference items

```{r}

frq(compulsive_exercisers$ED100k_ex_interfere_sum_complete)
```

The following variable defines presence of addictive exercise in the whole sample:

`ED100k_ex_addictive` (Having psychologically compulsive/driven exercise (feeling compelled to exercise or distressed if unable) that lasted for at least one month AND at least one life interfering symptom) 
```{r, echo=FALSE,message=FALSE}
frq(full_data$ED100k_ex_addictive)
```


And among the subsample who reported compulsive exercise (and were thus asked about life interfering symptoms): 

```{r}
frq(compulsive_exercisers$ED100k_ex_addictive)
```


### Excessive Exercise 

Excessive exercise was defined as compulsive exercise occurring for at least one month, every day or nearly ever day. Among the whole sample ('0' imputed for those reported no compulsive exercise), rates are:  

`ED100k_ex_excessive` (>1 month of compulsive exercise every day or nearly every day) 
```{r, echo=FALSE,message=FALSE}
frq(full_data$ED100k_ex_excessive)
```


Among the subsample who reported compulsive exercise, rates are: 

```{r, echo=FALSE,message=FALSE}
frq(compulsive_exercisers$ED100k_ex_excessive)
```


### Compensatory Exercise

All participants were asked about compensatory exercise (`be_icb__5`), with about half of the sample reporting compensatory exercise: 

```{r}
frq(full_data$be_icb___5)
```


### Broad Maladaptive Exercise

A broad maladaptive exercise variable was the final exercise variable made, which included individuals who reported 1 month of compulsive exercise OR any compensatory exercise -- 82% of the sample endorsed this history

`ED100k_ex_maladaptive_1mo` (reports 1 month of compensatory exercise OR any compensatory exercise)  
```{r, echo=FALSE,message=FALSE}
frq(full_data$ED100k_ex_maladaptive_1mo)